Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-20 manuscript/main.tex
added suffix array intro

\section{Suffix array construction}

>>>>

\section{Suffix array construction}
Suffix array is a permutation of string positions which lexicographically
sorts the suffixes of the string starting at that position.
It is extremely powerful data structure with many applications in efficient
algorithms on strings.
Enhanced by additional data structures, such as for example longest common
prefix (LCP) array, it can fully substitute suffix tree and solve problems,
such as exact pattern matching, repeat finding, maximum exact matching (MEM)
finding, document retrieval and many more.

There exists several algorithms for suffix array construction in linear time
\cite{} with several practical implementations \cite{}.
Altough their time complexity is linear, these algorithms become bottlenecks in
some application due to their linear space complexity.
This is especially relevant in pangenomics, where the datasets often do not fit
in the memory.
Nonetheless, as we shown in previous sections, prefix-free graphs can represent
the pangenome in substantialy smaller space and therefore can fit in computer
memory.

Here we show another crucial advantage of prefix-free graphs - their ability to
output the suffix array of the original string iterativelly.
This allows us to generate the suffix array one-by-one with the possibility
to compress or use in subsequential computations directly, giving us the ability
to use the rich theory of suffix arrays without ever storing them.
